---
title: "Sampling EDA"
author: "Grace Lawley"
date: "10/10/2018"
output: 
  html_document:
    theme: "cosmo"
    toc: true
    toc_float: true
    number_sections: true
---


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, warning = FALSE)
options(scipen = 999)

library(here)
library(tidyverse)
library(skimr)
library(kableExtra)
library(knitr)
```

# Load in the normalized tokens csv file
```{r}
normed_tokens <- read_csv(here("data", "processed", "post-norm_tokens.csv"))
```

# Deciding which _n_ to use for the samples:

Creating new dataframe with the token counts per corpus/child and adding a unique identifier for each corpus/child
```{r}
token_count <- normed_tokens %>% 
  count(corpus_name, target_child_name) %>% 
  rename(n_tokens = n) %>% 

  # adding unique id for each corpus/child
  group_by(corpus_name) %>%
  mutate(id = str_c(corpus_name, "_", row_number())) %>%
  ungroup() %>%
  select(id, everything())
```

Token Count, _Descending_
```{r}
token_count %>% 
  arrange(n_tokens) %>% 
  kable("html", caption = "Descending Token Count by Corpus/Child") %>% 
  kable_styling() %>% 
  scroll_box(width = "100%", height = "200px")
```

Token Count, _Ascending_
```{r}
token_count %>% 
  arrange(desc(n_tokens)) %>% 
  kable("html", caption = "Descending Token Count by Corpus/Child") %>% 
  kable_styling() %>% 
  scroll_box(width = "100%", height = "200px")
```

Output of `skimr::skim()`, a function for general summary statistics of a dataframe
```{r}
skim(token_count)
```

More general summary statistics of the token counts per corpus/child:
```{r}
token_count %>% 
  summarize(min = min(n_tokens),
            max = max(n_tokens),
            mean = mean(n_tokens),
            median = median(n_tokens),
            sd = sd(n_tokens),
            iqr = IQR(n_tokens)) %>% 
  kable(caption = "Summary Statistics for token count per corpus/child")
```

General summary statistics of the token counts per corpus/child with the Cornell corpus removed:
```{r}
token_count %>% 
  filter(corpus_name != "Cornell") %>% 
  summarize(min = min(n_tokens),
            max = max(n_tokens),
            mean = mean(n_tokens),
            median = median(n_tokens),
            sd = sd(n_tokens),
            iqr = IQR(n_tokens)) %>% 
  kable(caption = "Summary Statistics for token count per corpus/child")
```

Visualization of token count per corpus/child
```{r}
token_count %>%
  mutate(id = as.factor(id),
         id = fct_reorder(id, n_tokens)) %>% 
  ggplot(aes(id, n_tokens,
             fill = corpus_name)) +
        geom_col() +
        theme_minimal() +
        theme(axis.text.x = element_blank()) +
        labs(x = "Child", y = "# Tokens",
             title = "Token Count per Corpus/Child")

```

