---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# MacWhinney Corpus

#### Number of transcripts:
* Raw = 288
  + Contain two target children (see note) = 108
* Filtered = 120

#### Transcripts removed:  
* One file that was a handwritten diary
* Those where the child fell outside of the age range of 36-96 months

#### Number of utterances:
* Raw = 53,634
* Filtered = 19,637
* Processed = 19,395
  
#### Number of tokens & types:
* Tokens = 105,353
* Types = 4,325
* Type-Token Ratio = `r 4325/105353`

#### Top five most frequent tokens:
```{r echo = FALSE, message = FALSE}
library(readr)
library(knitr)
library(dplyr)

types <- read_csv('../../data/processed/macwhinney_type-count.csv')
head(types, n=5) %>% 
  kable(format = 'html', row.names = TRUE)

```



#### <span style="color:red">Note!</span>
When there are two target children in a sample, the `target_child_name`, `target_child_sex`, `target_child_age`, and `target_child_id` variables default to `NA`. The name of the child speaking is tracked in the `speaker_name` variable, but the age, sex, or id of the child speaking is *not* tracked. These transcripts are removed during the `02_macwhinney_filter-transcripts.R` when filtering for matches to the age range criterion.


