---
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Weist Corpus

#### Number of transcripts:
* Raw = 183
  + Untranscribed = 3
  + Mismarked 'role' = 28
* Filtered = 99

#### Transcripts removed:  
* Those where the child fell outside of the age range of 36-96 months

#### Number of utterances:
* Raw = 46,766
* Filtered = 24,863
* Processed = 24,539
  
#### Number of tokens & types:
* Tokens = 116,390
* Types = 4,162
* Type-Token Ratio = `r 4162/116390`

#### Top five most frequent tokens:
```{r echo = FALSE, message = FALSE}
library(readr)
library(knitr)
library(dplyr)

types <- read_csv('../../data/processed/weist_type-count.csv')
head(types, n=5) %>% 
  kable(format = 'html', row.names = TRUE)

```


#### <span style="color:red">Note!</span>
For 28 of the 183 raw transcripts, the 'role' of the target child is marked as 'Child', rather than the expected 'Target_Child'. Because of this, information about the target child's age, sex, and id are marked as 'NA'. To remedy this, 'Child' is included in as an option for 'role' in `get_utterances()`, in `01_weist_get-utterances.R`. The missing values were then reconstructed in `01_weist_filter-transcripts.R`. The reconstructed ages did not take into account days, only months and years.

Also, 3 of the transcript files did not have a transcription attached to them and were subsequently removed during the filtering step.

